---
title: "Predicting a Car's Miles Per Gallon (MPG)"
author: "Sanjay Lonkar"
date: "29 December 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Synopsis

* Course project of week 4 of Developing Data Products
* Demontrates a Shiny application (server.R & ui.R) deployed on Rstudio's shiny server
* Easy to use web application. User can select Transmission Type, Number of Cylinders, Weight of Car and Horse Power to get predicted Miles Per Gallon (MPG)
* URL to access this Shiny application is <https://sanjaylonkar.shinyapps.io/mtCarsPredictMPG/>


## Implementation Details

* mtcars dataset is referred to predict Miles Per Gallon (MPG)
* Application uses Multiple Linear Regression (MLR) model to predict MPG for given Transmission Type , Number of Cylinders , Weight of Car and Horse Power predictors
* Key Prediction Steps

1. Fit linear model: mFit = lm (mpg ~ am + cyl + wt + hp, data=mtcars)
2. Set predictors in a data frame: newCarPredictors = data.frame (am=as.numeric(input$ Trans), cyl = as.numeric(input$ Cyl), wt = as.numeric(input$ Weight), hp=as.numeric(input$ HP))
3. Predict MPG: newCarPredictedMPG  <- predict (mFit, newCarPredictors)


## Sample R Code Used in development of application

```{r echo = TRUE}

# Fit linear model
mFit = lm (mpg ~ am + cyl + wt + hp, data=mtcars)
# Set am + cyl + wt + hp
newCarPredictors = data.frame (am=1, cyl = 4, wt = 2, hp=80)
# PRedict MPG
newCarPredictedMPG  <- predict (mFit, newCarPredictors)
newCarPredictedMPG

library(ggplot2)
plotMPGtoCYL <- ggplot(mtcars, aes(cyl, mpg)) + labs (x = "Number of Cylinders", y = "Miles Per Gallon (MPG)", title = "MPG to Number of Car Cylinders") + geom_point() + geom_smooth (method="lm", color="Green")
print (plotMPGtoCYL)
```

## References

* Shiny application - <https://sanjaylonkar.shinyapps.io/mtCarsPredictMPG/>
* GitHub Repo - <https://github.com/celesto17/mtCarsPredictMPG>
* Slidy Presentation - <http://rpubs.com/Celesto17/mtCarsPredictMPG>

Thank You!!!

